The problem and promise of scale in multilayer animal social networks

### 2020-02-14 paper/manuscript.Rmd
need data.table (always)
update socres fig cap

DT <- readRDS('../data/derived-data/1-sub-seasons-fogo-caribou.Rds')
```

@@

<!-- Figure: metrics by social scale -->
(ref:socres) Varying scale in social threshold. For each social threshold, multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]`) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forest, forage, and open). A) Mean graph strength across individuals showed an increase for winter network layers at 50 m through 500 m while summer network layers had consistently weak connections. B) Mean layer relevance was relatively stable across social thresholds for each season and landcover layer. C) Similarity of landcover network layers between seasons (e.g. open summer compared to open winter) showed different responses to changing landcover scale with an overall increase in similarity for open layers and decrease in similarity for forage layers. <!--TODO: what about forest.--> D) Mean connective redundancy across individuals increased rapidly between 5 m and 50 m reaching a plateau of about 0.65 at approximately a 50 m <!--TODO:**??**--> social threshold before decreasing between 400 m and 500 m.

>>>>

library(data.table)
DT <- readRDS('../data/derived-data/1-sub-seasons-fogo-caribou.Rds')
```

@@

<!-- Figure: metrics by social scale -->
(ref:socres) Varying scale in social threshold. For each social threshold, multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]`) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forest, forage, and open). A) Mean graph strength across individuals showed an increase for winter network layers while summer network layers had consistently weak connections. B) Mean layer relevance was increased for winter layers between 5 m and 50 m, otherwise stable for all social thresholds >50 m for winter and all social thresholds for summer. C) Similarity of network layers across seasons and within habitat classes (e.g. open summer compared to open winter) was relatively stable for all habitat class layers. D) Mean connective redundancy across individuals showed an increase between 5 m and 50 m before remaining stable through all other social thresholds.
